Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
Cosmetic changes.
[ paper ] fixed typos in resolve.

First, we define \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
to convert a disjunction or a conjunction into its right-associative form.
The square symbol (⬓) can be the conjunction symbol or the disjunction symbol.
We use $\fassoc_{∧}$ to convert conjunctions and $\fassoc_{∨}$ for
disjunctions.

@@

The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or}
intends to construct a disjunction from another disjunction, specifically,
this functions will try to rearrange the disjuncts in the source formula to
match with the target disjunction formula.

@@

\begin{mainth}
  \label{thm:resolve}
  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, let $ℓ$ be a literal $ℓ : \Lit$, and $ψ : \Target$ then
  $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}

>>>>

First, we define the \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
to convert a disjunction or a conjunction into its right-associative form.
The square symbol (⬓) can be the conjunction symbol or the disjunction symbol.
We use $\fassoc_{∧}$ to convert conjunctions and $\fassoc_{∨}$ for
disjunctions.

@@

The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or}
intends to construct a disjunction from another disjunction, specifically,
this function will try to rearrange the disjuncts in the source formula to
match with the target disjunction formula.

@@

\begin{mainth}
  \label{thm:resolve}
  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}
